The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-07-10 manuscript/manuscript.tex
Push before circulate

\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{4}, Malte Schramm\altaffilmark{4}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{5}, Knud Jahnke\altaffilmark{6}, {\color{blue} Federica Duras\altaffilmark{7, 8}, Angela Bongiorno\altaffilmark{8}}
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{3}{{\color{blue} Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}}
\altaffiltext{4}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
\altaffiltext{5}{Korea Astronomy and Space Science Institute, Deajeon, 34055, Republic of Korea}
\altaffiltext{6}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117, Heidelberg, Germany}
\altaffiltext{7}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{8}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\begin{abstract}

The correlations between the mass of a supermassive black hole (SMBH) and its host galaxy properties (e.g. stellar mass \smass, luminosity \lhost) suggests an evolutionary connection. A powerful test of this co-evolution hypothesis is to measure the relations \mbh-\lhost\ and \mbh-\smass~(total) at high redshift and compare with the local relation. For this purpose, we obtained multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ emission, we obtained accurate measurements of the host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on near-infrared spectroscopic observations of the broad \halpha~line, which avoids potential uncertainties associated with \Mgii\ or \Civ\ .
%We find that the observed ratio of \mbh/\smass ~is 0.0035, a 0.24~dex offset as compared to the local relation that would lead to a evolution as \mbh/\smass$\propto(1+z)^\gamma$ with $\gamma = 0.80\pm0.30$. However, we expect an offset of 0.21 dex at these redshifts due to a selection bias thus the high-$z$ sample is consistent with the local sample if considering this effect. This is in agreement with the lack of evolution seen in the \mbh/\lhost ~ratios of our sample. Therefore, our results depict a scenario where SMBHs and their host galaxies co-evolve with the possibility for SMBHs to have slightly elevated masses, considering the observed ratios, that may indicate that galaxies with lower angular momentum at high-$z$ may be a bit more efficient to grow their black holes at earlier cosmic times. In any case, the bulge \smass ~mass at a given black hole mass is clearly discrepant with the local relation, since the hosts have a significant amount of stellar mass in a disk, thus leaving the open question as to whether the connection to the bulge is relevant for black hole growth.
{\color{blue}
We find that the observed ratio of \mbh/\smass is larger at $z\sim1.7$ than the one in the local universe. However, when accounting for the selection effect (using two independent methods), we find that the high redshift points can be consistent with the local relation, assuming the scatter is unchanged or larger. The relationship between \mbh\ and host galaxy total luminosity paints a similar picture: the ratio is larger than the local universe, but given the uncertainties and selection effects one cannot conclude that the offset is significant. Therefore, given the uncertainties, our results are consistent with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former is somewhat anticipated. Considering that the local relationships general apply to bulges, and our hosts have a significant amount of stellar mass in a disk, observations are consistent with a scenario in which stellar mass and luminosity is transferred from the angular momentum supported to the pressure supported component of the galaxy by secular processes or minor mergers at a faster rate than that of mass accretion onto the SMBH.
}

@@

Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass) and stellar velocity dispersion (\sigstar). These tight correlations (known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc). On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering {\color{blue} either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}}.
On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from galaxy assembly (i.e., mergers) which can reproduce the observed correlations.

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}. During the past decade, there has been much progress on this front at $z<1$ using type-1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today. Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations. Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach has not yet been well established. If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.

However, there are studies \citep{Cisternas2011,SS13,Mechtley2012} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation. In support, \citet{Sun2015} has re-analyzed the mass ratios for BLAGN in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citep{Merloni2010} and finds no evolution when accounting for selection effects \citep{Schulze2014} that consider the black hole mass functions and Eddington rate distribution. As highlighted below, samples based on 2D image analysis using \hst\ at $z>1$ are limited thus the infrared capabilities of \hst/WFC3 have not been fully exploited to date on this topic.

In order to make progress, it is important to reduce as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed AGNs, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}. For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.

@@

The AGN sample is initially detected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. More recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. We refer the reader to that paper for the details of continuum fitting and emission-line modeling.

Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$. The bolometric luminosities presented in \citet{Schulze2018} are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$. We are able to select the sample which have higher Eddington ratios when \mbh\ is lower, to assure the AGN is still activate, as shown in Figure~\ref{fig:selection}. Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007}. We list all the AGN systems analyzed in this work (Table~\ref{tab:objlist}).

%\subsection{Black hole mass and Eddington ratios}
\begin{figure}
\centering
{
\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
}
\caption{\label{fig:selection} 
We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$) and \mbh. Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}. We also control the sample to have higher Eddington ratios when their \mbh\ is lower, to guarantee the AGN activity. For comparing propose, we plot the high-$z$ luminous SDSS QSO samples that has been studied based on the observation of \hst\ in the reference~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}. 
}
\end{figure}

\begin{deluxetable*}{llccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Details of Observation} 
\tablehead{ 
\colhead{Object ID} &
\colhead{$z$} & 
\colhead{WFC3/Filter} &
\colhead{$RA$}&
\colhead{$DEC$}&
\colhead{Observing date}&
\colhead{Exposure time (s)}
\\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
\enddata
\label{tab:objlist}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
Column 6: The observing start date.
Column 7: Total exposure time.
}
\end{deluxetable*}

Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios. It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift avoiding bias ~\citep{Schulze2011, Tre++07, Bennert++2011, Park15}. The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (like AGN luminosity and line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors.

Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.

In order to get a sense for the amount of bias that we can anticipate given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias. In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to observations. The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function and Eddington ratio distribution at the redshift of observation. The latter two quantities are estimated from the type-1 AGN distributions corrected to represent the parent population of all SMBH hosts, including the inactive ones.

Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model. {\bf TT: we should say something about the uncertainty here for example the following.} This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs. Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends. We will revisit these issues in Section~\ref{select_eff}.

@@

To avoid any systematic bias between samples in the literature, we compare the recipes implemented in \citet{Schulze2018} and \citet{Ding2017b}. We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s. $<0.03$~dex) between the two reference samples. We also find that the cross-calibration between the \halpha\ and \hbeta\ has better agreement in \citet{Schulze2018}. Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :

@@

Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for 29 of our 32 AGNs. The remaining three (i.e. CDFS-1, CDFS-229 and CDFS-724) have information on their \halpha\ emission lines provided by \citet{Suh2015}. While fourteen AGN have emission line properties for both \halpha\ and \hbeta\, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample. It is worth noting that the absolute flux calibration of the FMOS spectra is set to match ground-based IR imaging, ULTRAVISTA in the case of COSMOS thus amounting to an effective aperture correction. While most recipes are calibrated against \hbeta\, the line is typically weaker than H$\alpha$, hence of lower signal-to-noise. We provide the \mbh\ measurements together with the properties of the emission lines in Table~\ref{tab:result_mbh}.

>>>>

\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{4}, Malte Schramm\altaffilmark{4}, Simon Birrer\altaffilmark{1}, Daeseong Park\altaffilmark{5}, Knud Jahnke\altaffilmark{6}, ???, ??? % {\color{blue} Federica Duras\altaffilmark{7, 8}, Angela Bongiorno\altaffilmark{8}}
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo, Kashiwa, Chiba 277-8583, Japan}
\altaffiltext{4}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
\altaffiltext{5}{Korea Astronomy and Space Science Institute, Deajeon, 34055, Republic of Korea}
\altaffiltext{6}{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117, Heidelberg, Germany}
%\altaffiltext{7}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
%\altaffiltext{8}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\begin{abstract}

Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g. stellar mass \smass, luminosity \lhost) suggest an evolutionary connection. A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates. For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ emission, we measured the host galaxy luminosity and stellar mass along with other properties through 2D model fitting. The black hole mass (\mbh) is determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators. We find that the  {\it observed} ratio of \mbh/\smass~is larger at $z\sim1.5$ by a factor of $\sim2.2$ as compared to that in the local universe, while the scatter is as low as in the local universe. However, when accounting for selection effects (estimated using two independent and complementary methods), we find that no-evolution is consistent with the data at the 95\% CL, both using our sample by itself and in combination with literature data. The relationship between \mbh\ and host galaxy total luminosity paints a similar picture. Therefore, given the uncertainties, our results are in agreement with a scenario where SMBHs and the total host stellar mass and luminosity proceed in lockstep or the growth of the former is somewhat slightly anticipated. Using a mass-matched sample of inactive galaxies to infer the bulge-to-total mass fraction we show that the bulge \mbh/\bmass~relation is significantly offset from the local one by a factor of $\sim4.5$; this offset is still present even after accounting for selection effects. Thus, our observations are consistent with a scenario in which stellar mass is transferred from an angular momentum supported to the pressure supported component of the galaxy through secular processes or minor mergers at a faster rate than the mass accretion onto the SMBH.

@@

Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass) and stellar velocity dispersion (\sigstar). These tight correlations (known as scaling relations) may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc). On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}.
On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from galaxy assembly (i.e., mergers) which can reproduce the observed correlations.

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}. During the past decade, there has been much progress on this front at $z<1$ using type-1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today. Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations, especially when the data are sufficiently good to isolate the luminosity or stellar mass of the bulge or spheroidal component. Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach for luminous AGNs has not yet been well established. If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.  A possible mechanism to account for the latter part of the growth of the galaxy without increasing \mbh\ is the transfer of stellar mass from the disk to the bulge \citep{Bennert++2011}.

However, there are studies \citep{Cisternas2011,SS13,Mechtley2016} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation. In support, \citet{Sun2015} has re-analyzed the mass ratios for BLAGN in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citet{Merloni2010} and finds no evolution when accounting for selection effects, as fully described in \citet{Schulze2014} that consider the black hole mass functions and Eddington rate distribution.

In order to make progress, it is important to construct statistical high-$z$ samples that reduce as much as possible the uncertainties, and carefully consider selection effects and inherent systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed AGNs, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}. For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.

@@

The AGN sample is initially detected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. We refer the reader to that paper for the details of continuum fitting and emission-line modeling.

Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$~(M$_{\odot}$). The bolometric luminosities presented in \citet{Schulze2018} are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$. The flux-limited nature of the sample results in higher Eddington ratios when \mbh\ is lower as shown in Figure~\ref{fig:selection}. Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007} and \citet{Koekemoer2007} in the COSMOS field and REFS for the (E)-CDF-S. We list the AGNs observed with \hst/WFC3 and analyzed in this work in Table~\ref{tab:objlist} sorted by field and redshift.

@@

%To avoid any systematic bias between samples in the literature, we compare the recipes implemented in \citet{Schulze2018} and \citet{Ding2017b}. We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s. $<0.03$~dex) between the two reference samples. We also find that the cross-calibration between the \halpha\ and \hbeta\ has better agreement in \citet{Schulze2018}. Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :

To avoid any systematic bias between samples in the literature, we aim to adopt a class of self-consistent estimators for our sample. We first compare the estimators implemented in \citet{Schulze2018} to the those in \citet{Ding2017b}, and find that their \hbeta(FWHM(5100)) estimators are very consistent (\mbh\ r.m.s. $<0.03$~dex). However, there is a $\sim~0.2$~dex inconsistency in their \halpha\ estimators. Thus, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has been agreement between the two lines. As a  result, the \halpha\ estimator in \citet{Schulze2018} has better agreement with \hbeta\  . Thus, we adopt the scheme given in \citet{Schulze2018} for all AGN samples used in this study including the comparison samples described below.

@@

Using these recipes, we estimate \mbh\ by adopting the emission-line properties as measured by \citet{Schulze2018} for all 32 AGNs. The three objects (i.e. CDFS-1, CDFS-229 and CDFS-724) have infrared spectra provided by \citet{Suh2015}. While fourteen AGN have emission line properties for both \halpha\ and \hbeta, we adopt the value of \mbh\ based on the \halpha\ emission line to have consistency across the sample. It is worth noting that the absolute flux calibration of the FMOS spectra is set to match ground-based IR imaging, ULTRAVISTA in the case of COSMOS thus amounting to an effective aperture correction. While most recipes are calibrated against \hbeta\, the line is typically weaker than H$\alpha$, hence of lower signal-to-noise. We provide the \mbh\ measurements together with the properties of the emission lines in Table~\ref{tab:result_mbh}.

Our AGN sample is primarily selected based on the value of \mbh~and Eddington ratio. It is well known that sample selection effects must be taken into account in order to  interpret the observed black hole-host relations and measure its evolution with redshift thus avoiding well understood biases ~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}. The main source of bias is due to the fact that active samples are necessarily selected based on properties that correlate with black hole mass estimators (like AGN luminosity and line strength and width) and thus one tends to favor overly massive black holes in presence of intrinsic scatter and observational errors. Correcting for observational biases requires a well-characterized selection function, such as the one we have for our sample, and a model of the black hole mass function, and the evolution of the correlations between \mbh, and other properties.

To assess the amount of bias that we can anticipate given our selection function, we use the Bayesian framework introduced by \citet{Schulze2011,Schulze2014} to estimate the expected bias. In this framework, under the assumption of no evolution of the correlations between \mbh\ and host-galaxy properties, one can compute the expected bias for a given sample, prior to the observations. The key ingredient of this model are the local \mbh\ host-galaxy property correlations, the black hole mass function and Eddington ratio distribution at the redshift of observation. The latter two quantities are estimated from the type-1 AGN distributions \citep{Schulze2015} and corrected to represent the parent population of all active SMBH hosts thus including the obscured cases.

Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model. This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs. Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends. We will revisit these issues in Section~\ref{select_eff}.
